PyUltraLight: A Pseudo-Spectral Solver for Ultralight Dark Matter Dynamics

### 2018-05-29 draft.tex
Richard, through to p8
Richard, through to section 4.2

%\re{read to here}
Given the presence of a fundamental  lengthscale, the behaviour of ULDM is more complex than that of simple dark matter scenarios whose cosmologically relevant interactions are purely gravitational. Physically, the effective short-scale pressure and  condensate-like properties of ULDM  create new dynamical possibilities for ULDM scenarios, such as  purely pressure supported soliton-like solutions  \cite{Marsh2015} and superposition or interference during interactions between condensate-like halos \cite{Schwabe2016}. Consequently, modelling dark matter dynamics in ULDM scenarios is more challenging than in simple cold dark matter models, but is critical to understanding the physical consequences of ULDM models.

@@

Evaluation of equation \ref{eq:split-step} within \PyUltraLight thus proceeds as follows:
Initially, the nonlinear term acts in position space for one half-timestep. The result is  Fourier transformed, and a full timestep is taken with the differential operator  applied in the Fourier domain. The potential field is then updated in accordance with equation \ref{eq:p-adim}. After an inverse Fourier transform a final half timestep is taken with the updated nonlinear term acting in position space to give the new $\psi$ field configuration. This procedure is known as the symmetrised split-step Fourier method, and  used widely in fields such as nonlinear fiber optics \cite{Agrawal2013}. \re{do want a couple of other examples/cites?}

@@

\PyUltraLight specifies the initial dark matter configuration as a superposition of an arbitrary number of solitonic halos, with arbitrary (user-defined) velocities and phases. This is necessarily an idealisation, given that realistic dark matter halos will not map directly to the solitonic solutions, but it provides an excellent ``playground'' in which to explore ULDM dynamics, and the initialisation routines within \PyUltraLight can be easily augmented to accommodate a wider range of scenarios. The initial field configuration is built by loading a NumPy array file encoding a solitonic solution to the Schr{\"o}dinger-Poisson system and the corresponding position mass, velocity, and phase parameters each specified by the user within the accompanying Jupyter notebook. In practice, only a finite  range of halo masses can be supported within a given simulation -- the  radius of a solitonic halo is inversely proportional to it mass, so resolve a light halo interacting with a very massive halo would require an extremely fine spatial mesh. \re{is there a power to this, or $r \sim 1/M_{halo}$?} \re{to here}

The solitonic solution to the SP system is a natural choice of initial field configuration; these stable, localised objects are ubiquitous in ULDM models \cite{Marsh2015}.

%In particular, it is proposed that ULDM halos exhibit Navarro-Frenk-White profiles at large radii, with solitonic cores at smaller radii. Because solitons have a constant central density, it is suggested that this offers a solution to the core-cusp problem of $\Lambda$CDM \cite{Marsh2015}.

%Remove this section if we're going to talk about solitons merging to form NFW/soltion profiles, and compare to e.g. Schwabe.

In this section, we discuss the method used to generate the soliton profile. Following \cite{Paredes2016}, we begin by assuming a spherically symmetric solution to the SP system:
\begin{equation}
    \psi(\vec{x},t)\rightarrow e^{i\beta t} f(r), \quad \Phi(\vec{x},t)\rightarrow \varphi(r),
\end{equation}
where $r=\vert\vec{x}\vert$. Introducing $\tilde{\varphi}(r):=\varphi(r)+\beta$, equations \ref{eq:s-adim} and \ref{eq:p-adim} are reduced to
\begin{align}
    0 &= -\frac{1}{2}f^{\prime\prime}(r)-\frac{1}{r}f^\prime(r)+\tilde{\varphi}(r)f(r)\label{eq:s-spherical}\\
    0 &= \tilde{\varphi}^{\prime\prime}(r)+\frac{2}{r}\tilde{\varphi}^\prime(r)-4\pi f(r)^2\label{eq:p-spherical}
\end{align}
where primes denote derivatives with respect to $r$. To generate profiles for $\tilde{\varphi}(r)$ and $f(r)$ which satisfy these equations, we use a fourth-order Runge-Kutta algorithm, included as the auxiliary soliton\texttt{\_}solution.py program. We make the arbitrary choice $f(r=0)$=1, while the smoothness criterion demands that the first derivatives of $f(r)$ and $\tilde{\varphi}(r)$ vanish at the origin. We then search for solutions of $f(r)$ and $\varphi(r)$ which satisfy the boundary conditions $\operatorname{lim}(r\rightarrow\infty)\varphi(r)=0$ and $\operatorname{lim}(r\rightarrow\infty)f(r)=0$. To do this we use a shooting method, varying $\tilde{\varphi}(r=0)$ until we obtain a solution of $f(r)$ which approaches zero at the maximal specified radius, $r_m$. The value of $\beta$ is then calculated by assuming that $\varphi(r)$ goes as $-c/r$ at large radii, where $c$ is a constant. Under this assumption, we can write
\begin{equation}
    \tilde{\varphi}(r_m)=-\frac{c}{r_m}+\beta, \quad c=r_m^2\tilde{\varphi}^{\ \prime}(r_m).
\end{equation}
We thus obtain the full solution $\psi(\vec{x},t)=e^{i\beta t}f(r)$.
Having initially chosen $f(r=0)=1$, we may then generalise to $f(r=0)=\alpha$, where $\alpha$ is an arbitrary positive real number. It is easy to verify that if $e^{i\beta t}f(r)$ is a solution to the spherically symmetric SP system, then $g(r)$ is also a solution, where
\begin{equation}
    g(r)=e^{i\alpha\beta t}\alpha f(\sqrt{\alpha}\ r).
\end{equation}
Hence we obtain a family of spherically symmetric soliton solutions to the dimensionless SP system, for which the dimensionless soliton mass is proportional to $\sqrt{\alpha}$ and the full width at half maximum is proportional to $1/\sqrt{\alpha}$. Because the size of the soliton scales inversely with the mass, it is important to consider the maximum soliton mass which can be accurately modeled in a simulation with finite spatial resolution.

While the Schr{\"o}dinger equation is not trivially form invariant under Galilean boosts, we can enforce Galilean covariance by augmenting the solutions through the addition of a velocity-dependent phase factor. Namely,
\begin{equation}\label{eq:covariant-solution}
    \psi(\vec{x},t)=\alpha f\big(\sqrt{\alpha}\vert\vec{x}-\vec{v}t\vert\big)e^{i\left(\alpha\beta t+\vec{v}\cdot\vec{x}-\frac{1}{2}\vert\vec{v}\vert^2t\right)}.
\end{equation}
To construct the initial field configuration within \PyUltraLight, the NumPy array encoding the radial profile $f(r)$ for the $f(r=0)=1$ case is loaded, where the spatial resolution of this profile must agree with the expected spatial resolution within the main code. Equation \ref{eq:covariant-solution} is then used to augment the configuration such that the soliton is furnished with the position, mass, and velocity specified by the user in the accompanying Jupyter notebook. The user may also add an additional constant phase factor if desired.

While the current implementation of \PyUltraLight is designed such that the initial field configuration is built from solitons, it may be simply modified to take in alternative field configurations in future.

@@

When using finite-differencing methods to solve certain partial differential equations, the causality-preserving Courant-Friedrichs-Lewy (CFL) condition on the size of the simulation timestep is a necessary condition for convergence \cite{Ajaib2013}. As such, this condition is often appears in numerical analysis of ULDM physics governed by the SP system, an example being \cite{Schwabe2016}. However, because \PyUltraLight does not use the method of finite differences to compute spatial derivatives, but rather computes them exactly via explicit multiplication in the Fourier domain, the CFL condition in its usual formulation is not applicable to this code.

In place of the CFL condition, the constraint on the timestep within \PyUltraLight is set based on the fluid interpretation of the SP system. In dimensionless code units we can write 
\begin{equation}
    \psi\equiv\sqrt{\rho}e^{i\theta}, \quad \vec{v}\equiv\boldsymbol{\nabla}\theta.
\end{equation}
From here we can define a `maximum velocity' for the simulation grid. This is the velocity at which the fluid appears to move backward, which occurs when the phase change between successive grid points exceeds $\pi$. The timestep is then constrained such that a fluid travelling at this maximum grid velocity will traverse a distance of one grid space per timestep.

This proves to be a highly restrictive constraint on the timestep, and can be relaxed significantly at the user's discretion for simulations in which the expected velocities within the system will not approach this maximum grid velocity. Convergence testing on a case-by-case basis is encouraged to determine the timestep constraint necessary for a given degree of accuracy.

\section{Verification of ULDM Dynamics}\label{sec:test}

In this section we test the validity of \PyUltraLight as a numerical SP solver by reproducing a number of results from previous studies of ULDM dynamics. We are able to reproduce phenomena arising due to the wavelike nature of ULDM, namely interference effects and effective repulsive forces. Additionally, we study the evolution of the velocity field within a solitonic core orbiting within a Newtonian central potential, showing that in the absence of complete tidal disruption, the stable orbital configuration is one of an irrotational Riemann-S ellipsoid. Finally, we demonstrate sub-percent level energy conservation for a selection of dynamical scenarios.

@@

Hierarchical structure formation within the ULDM framework proceeds through both gravitational overdensity collapse as well as through sequential binary mergers of solitonic cores to form individual virialised objects \cite{Schive2014}. It is therefore important that ULDM simulations are able to accurately reproduce the expected characteristics of binary soliton interactions.

Soliton collisions can be classified into two categories depending on whether the total energy of the isolated binary system is positive or negative. In the case of positive energy, the solitons pass through each other, emerging largely undisturbed from their initial configurations following the interaction. During the collision, the wavefunctions describing the solitons are superposed, yielding distinctive interference patterns. In this section we demonstrate the ability of \PyUltraLight to reproduce the interference patterns predicted by theoretical models during binary collisions.

Following \cite{Schwabe2016}, we consider the head-on collision of two solitions with mass ratio $\mu=2$ and high relative velocity. Using equation \ref{eq:covariant-solution}, we can write the total wavefunction of the binary system in terms of dimensionless quantities along the collision axis as
\begin{align}
    \psi(x,t)=& \ \alpha_1 f\big(\sqrt{\alpha_1}\vert x-x_1-v_1 t\vert\big)e^{i\left(\alpha_1\beta t+v_1(x-x_1)-\frac{1}{2}v_1^2 t+\delta\right)}\nonumber\\
    &+\alpha_2 f\big(\sqrt{\alpha_2}\vert x-x_2-v_2 t\vert\big)e^{i\left(\alpha_2\beta t+v_2(x-x_2)-\frac{1}{2}v_2^2 t\right)}
\end{align}
where $x_1$ and $x_2$ are the initial positions of the centres of the solitions, $v_1$ and $v_2$ are the velocities of the solitons, $\delta$ is a constant relative phase term, and $\alpha_1=1/4 \ \alpha_2$ parameterise the density profiles as discussed in section \ref{sec:soliton-profiles}. Because of the symmetry of the configuration, we take $v_1=-v_2$ and $x_1=-x_2$. We are interested in the density profile of the system at the time of maximal interference, where we expect the superposed wavefunction to possess pronounced features. Therefore, we choose the time at which the two components of the wavefunction are centred at the same location, such that $x_1+v_1t=-x_2-v_2t=0$. This corresponds to a time $t_{max}=\vert x_1/v_1\vert = \vert x_2/v_2\vert$. The dimensionless density is then given by
\begin{align}\label{eq:predicted-interference}
    \vert\psi(x,t_{max})\vert^2= \ \alpha_1^2\bigg[&f(\sqrt{\alpha_1}x)^2+16f(2\sqrt{\alpha_1}x)^2+\nonumber\\
    &8f(\sqrt{\alpha_1}x)f(2\sqrt{\alpha_1}x)\operatorname{cos}\left(-3\alpha_1\beta\left\vert\frac{x_1}{v_1}\right\vert+2v_1x+\delta \right)\bigg]
\end{align}
In Figure \ref{fig:interference}, we plot the dimensionless density profile at the time of maximal interference for two solitons with mass ratio $\mu=2$, and phase difference $\delta=0$. We see that the numerical result obtained using \PyUltraLight closely matches the theoretical prediction of equation \ref{eq:predicted-interference}. Small disparities between the numerical and theoretical profiles may be attributed to the effect of gravitational contraction not included in the theoretical prediction of equation \ref{eq:predicted-interference}, and to a small offset in the true time of maximal interference. Neglecting these small deviations, we can verify that the code is well suited to faithfully reproduce the wave interference effects of the ULDM model. 
\begin{figure}
  \includegraphics[trim={0 0 0 0.9cm},clip, scale=0.9]{interference_patterns}
  \caption{Comparison of theoretical and numerical density profiles at time of maximal interference for head-on collision of two solitons with mass ratio $\mu=2$ and no relative phase difference. The solitons were chosen with dimensionless masses 5 and 10, with an initial separation of 4 code units and relative velocity of 20 code units. The simulation was run at $256^3$ for a box of side-length 8 code units.}
  \label{fig:interference}
\end{figure}

>>>>

Given the presence of a fundamental  lengthscale, the behaviour of ULDM is more complex than that of simple dark matter scenarios whose cosmologically relevant interactions are purely gravitational. Physically, the effective short-scale pressure and  condensate-like properties of ULDM  create new dynamical possibilities for ULDM scenarios, such as  purely pressure supported soliton-like solutions  \cite{Marsh2015} and superposition or interference during interactions between condensate-like halos \cite{Schwabe2016}. Consequently, modelling dark matter dynamics in ULDM scenarios is more challenging than in simple cold dark matter models, but is critical to understanding the physical consequences of ULDM models.

@@

Evaluation of equation \ref{eq:split-step} within \PyUltraLight thus proceeds as follows:
Initially, the nonlinear term acts in position space for one half-timestep. The result is  Fourier transformed, and a full timestep is taken with the differential operator  applied in the Fourier domain. The potential field is then updated in accordance with equation \ref{eq:p-adim}. After an inverse Fourier transform a final half timestep is taken with the updated nonlinear term acting in position space to give the new $\psi$ field configuration. This procedure is known as the symmetrised split-step Fourier method, and  used widely in fields such as nonlinear fiber optics \cite{Agrawal2013}. \re{do we want a couple of other examples/cites?}

@@

\PyUltraLight specifies the initial dark matter configuration as a superposition of an arbitrary number of solitonic halos, with arbitrary (user-defined) velocities and phases. This is necessarily an idealisation, given that realistic dark matter halos will not map directly to the solitonic solutions, but it provides an excellent ``playground'' in which to explore ULDM dynamics, and the initialisation routines within \PyUltraLight can be easily augmented to accommodate a wider range of scenarios. The initial field configuration is built by loading a NumPy array file encoding a solitonic solution to the Schr{\"o}dinger-Poisson system and the corresponding position mass, velocity, and phase parameters each specified by the user within the accompanying Jupyter notebook.

In practice, only a finite  range of halo masses can be supported within a given simulation -- the  radius of a solitonic halo is inversely proportional to its mass, so resolving a light halo interacting with a very massive halo would require an extremely fine spatial mesh.  However, \PyUltraLight also allows the user to specify a fixed, external potential which does not take part in the dynamics. At this point only a central $1/r$ potential is supported but this would be easily generalised. \re{new material. Also, do we need to say anything about what happens when the solitions cross into the ``next" box?}

The soliton profile is found by imposing a spherically symmetric profile \cite{Paredes2016} where the radial profile is assumed to be time independent
%
\begin{equation}
    \psi(\vec{x},t)\rightarrow e^{i\beta t} f(r), \quad \Phi(\vec{x},t)\rightarrow \varphi(r),
\end{equation}
where $r=\vert\vec{x}\vert$. Introducing $\tilde{\varphi}(r):=\varphi(r)+\beta$, equations \ref{eq:s-adim} and \ref{eq:p-adim}  reduce to
\begin{align}
    0 &= -\frac{1}{2}f^{\prime\prime}(r)-\frac{1}{r}f^\prime(r)+\tilde{\varphi}(r)f(r)\label{eq:s-spherical}\\
    0 &= \tilde{\varphi}^{\prime\prime}(r)+\frac{2}{r}\tilde{\varphi}^\prime(r)-4\pi f(r)^2\label{eq:p-spherical}
\end{align}
%
where primes denote derivatives with respect to $r$. Note that this system contains no arbitrary constants, so the underlying profile will effectively be universal and \PyUltraLight loads a precomputed profile supplied with the code, rather than computing it from scratch each time the code is run. However, an auxiliary program {\sc soliton\texttt{\_}solution.py} is supplied with  \PyUltraLight; it uses a  fourth-order Runge-Kutta algorithm to solve the coupled profile equations. We set $\left. f(r) \right|_{r=0}$=1, while  smoothness requires that first derivatives of $f(r)$ and $\tilde{\varphi}(r)$ vanish at the origin. We then use the shooting method to search for solutions of $f(r)$ and $\varphi(r)$  satisfying the boundary conditions $\lim_{r\rightarrow\infty}\varphi(r)=0$ and $\lim_{r\rightarrow\infty}f(r)=0$, varying $\left. \tilde{\varphi}(r)\right|_{r=0}$ until we obtain a solution of $f(r)$ which approaches zero at the maximal specified radius, $r_m$. The value of $\beta$ is then calculated by assuming that $\varphi(r)$ goes as $-c/r$ at large radii, where $c$ is a constant. Under this assumption, we can write
\begin{equation}
    \tilde{\varphi}(r_m)=-\frac{c}{r_m}+\beta, \quad c=r_m^2\tilde{\varphi}^{\ \prime}(r_m).
\end{equation}
We thus obtain the full solution $\psi(\vec{x},t)=e^{i\beta t}f(r)$.
Having initially chosen $\left. f(r)\right|_{r=0}=1$, we may then generalise to $\left. f(r)\right|_{r=0}=\alpha$, where $\alpha$ is an arbitrary positive real number. It is easily verified that if $e^{i\beta t}f(r)$ is a solution to the spherically symmetric Schr{\"o}dinger-Poisson system, then $g(r)$ is also a solution, where
\begin{equation}
    g(r)=e^{i\alpha\beta t}\alpha f(\sqrt{\alpha}\ r).
\end{equation}
We thus have a family of spherically symmetric soliton solutions to the dimensionless Schr{\"o}\-dinger-Poisson system; the dimensionless soliton mass is proportional to $\sqrt{\alpha}$ and the full width at half maximum is proportional to $1/\sqrt{\alpha}$. Since the size of the soliton scales inversely with the mass, the most massive soliton in the solution  puts a lower bound on the required spatial resolution.

The Schr{\"o}dinger equation is not trivially form invariant under Galilean boosts but we can enforce Galilean covariance through the addition of a velocity-dependent phase factor,
%
\begin{equation}\label{eq:covariant-solution}
    \psi(\vec{x},t)=\alpha f\big(\sqrt{\alpha}\vert\vec{x}-\vec{v}t\vert\big)e^{i\left(\alpha\beta t+\vec{v}\cdot\vec{x}-\frac{1}{2}\vert\vec{v}\vert^2t\right)}.
\end{equation}
%
To construct the initial field configuration,  \PyUltraLight, loads the NumPy array encoding the radial profile $f(r)$ for the $\left. f(r)\right|_{r=0}=1$ case. Equation \ref{eq:covariant-solution} is then used to transform the this solution into soliton(s) with user-specified values position, mass, and velocity specified, via the accompanying Jupyter notebook. The user may also add an additional constant phase factor if desired.

@@

In many finite-differencing schemes for  partial differential equations the Courant-Friedrichs-Lewy (CFL) condition is a necessary condition for convergence \cite{Ajaib2013}, and puts an upper bound on the timestep as  function of the gridsize whose physical origin is the finite speed of propagating information  in the evolving system.  Consequently, this condition is often cited in numerical analysis of ULDM physics governed by the Schr{\"o}dinger-Poisson system, see e.g. Ref.~\cite{Schwabe2016}. Strictly speaking, however, the CFL condition is applicable to codes using finite differencing methods for spatial derivatives, and is thus not applicable to pseudospectral codes like \PyUltraLight.   We also note that the Poisson equation is acausal in that it responds globally and instantaneously to local changes in the matter distribution. However, the Schr{\"o}dinger-Poisson equation is an approximation derived  in the nonrelativistic limit so this is not a shortcoming in regimes where the underlying equations are physically valid.

In place of the CFL condition, the \PyUltraLight timestep can be set via the fluid interpretation of the Schr{\"o}dinger-Poisson system. In dimensionless code units we can write 
\begin{equation}
    \psi\equiv\sqrt{\rho}e^{i\theta}, \quad \vec{v}\equiv\boldsymbol{\nabla}\theta.
\end{equation}
We define a `maximum velocity' for the simulation grid at which point the fluid appears to move backward because the phase change between successive grid points exceeds $\pi$. An upper bound can then be placed on the timestep so that a fluid travelling at this maximum  velocity  traverse a distance of one grid space per timestep.  In practice this can yield a very demanding constraint on the timestep and for many scenarios the actual velocity is far less than this hypothetical limit. Consequently, the timestep can be  significantly increased at the user's discretion but convergence testing on a case-by-case basis is strongly encouraged.

\section{ULDM Dynamics with \PyUltraLight}\label{sec:test}

In this section we validate \PyUltraLight a by reproducing results from previous studies of ULDM dynamics, demonstrating interference effects and effective repulsive forces arising from the wavelike nature of ULDM. In addition we study the evolution of the velocity field of a solitonic core orbiting within a Newtonian central potential, showing that the stable orbital configuration is an irrotational Riemann-S ellipsoid. Finally, we show demonstrate that \PyUltraLight delivers sub-percent level energy conservation for a selection of dynamical scenarios.

@@

\begin{figure}
  \includegraphics[trim={0 0 0 0.9cm},clip, scale=0.9]{interference_patterns}
  \caption{Comparison of theoretical and numerical density profiles at time of maximal interference for head-on collision of two solitons with mass ratio $\mu=2$ and no relative phase difference. The solitons were chosen with dimensionless masses 5 and 10, with an initial separation of 4 code units and relative velocity of 20 code units. The simulation was run at $256^3$ for a box of side-length 8 code units. \re{do we want to say something about how a code unit is defined for a velocity?}}
  \label{fig:interference}
\end{figure}

The outcomes of ULDM soliton collisions depend critically on  whether the total energy of the isolated binary system is positive or negative. With a positive total energy the solitons pass through each other, emerging largely undisturbed from their initial configurations and the wavefunctions describing the solitons are superposed during the collision,, yielding distinctive interference patterns.

Following \cite{Schwabe2016}, we consider the head-on collision of two solitions with mass ratio $\mu=2$ and high relative velocity. This simple case can be treated approximately. Starting from equation \ref{eq:covariant-solution} we  write the total wavefunction of the binary system in terms of dimensionless quantities along the collision axis as
\begin{align}
    \psi(x,t)=& \ \alpha_1 f\big(\sqrt{\alpha_1}\vert x-x_1-v_1 t\vert\big)e^{i\left(\alpha_1\beta t+v_1(x-x_1)-\frac{1}{2}v_1^2 t+\delta\right)}\nonumber\\
    &+\alpha_2 f\big(\sqrt{\alpha_2}\vert x-x_2-v_2 t\vert\big)e^{i\left(\alpha_2\beta t+v_2(x-x_2)-\frac{1}{2}v_2^2 t\right)}
\end{align}
where $x_1$ and $x_2$ are the initial centrals positions of the solitions, $v_1$ and $v_2$ are the soliton velocities, $\delta$ is a constant relative phase term and $\alpha_1=1/4 \ \alpha_2$, parameterising the density profiles as discussed in section \ref{sec:soliton-profiles}. For convenience we set $v_1=-v_2$ and $x_1=-x_2$. We expect that the interference effects will be maximised when two components of the wavefunction are centred at the same location, such that $x_1+v_1t=-x_2-v_2t=0$. This corresponds to a time $t_{o}=\vert x_1/v_1\vert = \vert x_2/v_2\vert$. The dimensionless density is then given by
\begin{align}\label{eq:predicted-interference}
    \vert\psi(x,t_{o})\vert^2= \ \alpha_1^2\bigg[&f(\sqrt{\alpha_1}x)^2+16f(2\sqrt{\alpha_1}x)^2+\nonumber\\
    &8f(\sqrt{\alpha_1}x)f(2\sqrt{\alpha_1}x)\operatorname{cos}\left(-3\alpha_1\beta\left\vert\frac{x_1}{v_1}\right\vert+2v_1x+\delta \right)\bigg]
\end{align}
 Figure \ref{fig:interference} shows the dimensionless density profile at the time of maximal interference for two solitons with mass ratio $\mu=2$ and phase difference $\delta=0$. The numerical result obtained using \PyUltraLight closely matches the theoretical prediction of equation \ref{eq:predicted-interference}. Small disparities between the numerical and theoretical profiles may be attributed to the effect of gravitational contraction not included in the theoretical prediction of equation \ref{eq:predicted-interference} and to a small offset in the true time of maximal interference \re{due to the solitons accelerating as they fall together?}. We do not expect an exact match, but we have verified \PyUltraLight qualitatively reproduce the wave interference effects of the ULDM model. \re{are there numerical treaments elsewhere we can compare to?}

\re{read to here}
